\cvsection{Experience}
\begin{cventries}
  \cventry
    {Undergraduate Research Assistant, Supervised by Professor Jesse Hoey}
    {University of Waterloo}
    {Waterloo, Canada}
    {2016. 1 - 2016. 5}
    {
      \begin{cvitems}
        \item {Research: Social Dilemmas: From Rational to Human Perspectives.}
        \item {Started from a purely rational standpoint to human solutions and the evolution of cooperation. Completed a paper review based on twelve related publications in biology, psychology and computer science area.}
        \item {Apply humans' emotions and social interactions to intelligence machine. Test on Iterated Prisoner's Dilemma Game. Better performance than traditional tit-for-tat agent. Similar behavior graph compared with human players.}
        \item {Plan to hold a social dilemma tournament in October which invite people from any area worldwide to participate. Further exploration in human-computer Turing test where agents play Prisoner's Game based on human expression analysis.}
      \end{cvitems}
    }
  \cventry
    {Undergraduate Course: Artificial Neural Networks}
    {Tsinghua University}
    {Beijing, China}
    {2015. 9 - 2015. 1}
    {
      \begin{cvitems}
        \item{Project: Pattern Recognition}
        \item{Implemented neural network models without the help of neural network tools such as Caffe or Theano to classify CIFAR-10 dataset of 60,000 color images in 10 classes.}
        \item{Applied neural network with fully connected layers(MLP) and convolutional neural network(CNN) to classify the images and received the accuracy rate of more than 90 percents and 70 percents respectively.}
        \item{Combined neural network with fully connected layers and support vector machine(SVM) to increase the accuracy rate by 5 percents.}
      \end{cvitems}
    }
  \cventry
    {Undergraduate Course: Introduction to Machine Learning}
    {Tsinghua University}
    {Beijing, China}
    {2015. 2 - 2015. 6}
    {
      \begin{cvitems}
        \item{Project: Decision Tree Algorithm}
        \item{Implemented decision tree to help bank decide whether a person's income exceed a certain amount based on related data.}
        \item{Handled missing data and numerical attributes differently and properly with C4.5 decision tree algorithm. Trained a post-pruned decision tree to avoid overfitting problem. Received an accuracy rate of more than 85 percents.}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Tencent}
    {Shenzhen, China}
    {2015. 7 - 2015. 8}
    {
      \begin{cvitems}
        \item {Developed Online Poster Maker Application. Written in php + SQL on the server end and HTML5 + CSS + javascript on the front end. Implemented in Lithium MVC Framework. Added animation effects and background music to make posters more attractive.}
        \item {Enabled users to create a series of posters easily with provided templates for specific scenes, generate web pages and share with friends and teammates online. Could be used as lightweight PowerPoint in life and work.}
        \item {The application is now used for official accounts management supported by Wechat(one of the popular social applications in China).}
      \end{cvitems}
    }
  
\end{cventries}
